Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1) \note{\scriptsize Authors, please add/check middle initials and affiliations}

### 2014-04-11 WSSSPE1_report/WSSSPE1_summary_report.tex

>>>>

Several papers presented discussed the connection between industry and
scientific software, from the perspective of both integrating efforts between
the two and sustaining long-term development.

Foster et al.~\cite{Foster_WSSSPE} discussed the approach of developing sustainability models
around Software-as-a-Service (SaaS) platforms, with the target example being
that of GlobusOnline.  The authors build a case that both grant-based and
volunteer-based development fall short in sustaining software, resulting in
software that is disproportionately difficult to use compared to its
functionality, which they note directly impacts the overall scientific
productivity of its users.  In contrast, by charging a subscription fee for
hosted, centrally-managed software (similar to offerings by Dropbox, EverNote,
GMail), the authors propose to manage the funding cycle and enable a greater
focus on the aspects of software that directly impact individuals, rather than
funders.  Globus has deployed such a service, for which they have attempted to
develop a sustainable economic model that reduces institutional obstacles to
funding and subscription.  However, they do identify that cultural obstacles
do still remain, and they note a particular difference in culture between NSF-
and NIH-funded researchers.
